---
jupyter:
  jupytext:
    text_representation:
      extension: .Rmd
      format_name: rmarkdown
      format_version: '1.2'
      jupytext_version: 1.10.3
  kernelspec:
    display_name: R
    language: R
    name: ir
---

# R lab exercises - Set 7

```{r}
# ** Libraries and packages **
    library(tidyverse)
    library(lubridate) 
    library("ggpubr")
    #install.packages('GoFKernel')
    library('GoFKernel')
    #install.packages('dplyr')
    library(dplyr)
    library(scales)
    library(reshape2)
```

## Exercise 1

A well established and diffused method for detecting a disease in blood fails to detect the presence of disease in $15\%$ of the patients that actually have the disease.

A young UniPD startUp has developed an innovative method of screening. During the qualification phase, a random sample of $n = 75$ patients known to have the disease is screened using the new method.

**(a)** What is the probability distribution of $y$, the number of times the new method fails to detect the disease?

**(b)** On the $n = 75$ patients sample, the new method fails to detect the disease in $y = 6$ cases. What is the frequentist estimator of the failure probability of the new method?

**(c)** Setup a bayesian computation of the posterior probability, assuming a beta distribution with mean value $0.15$ and standard deviation $0.14$. Plot the posterior distribution for y, and mark on the plot the mean value and variance.

**(d)** Perform a test of hypothesis assuming that if the probability of failing to the detect the disesease in ill patients is greater or equal than $15\%$, the new test is no better that the traditional method.
Test the sample at a $5\%$ level of significance in the Bayesian way.

**(e)** Perform the same hypothesis test in the classical frequentist way.


### Solution

**(a)** In this process there are only two possible outcomes: the new screening method either fails or succeeds in detecting the disease. We are thus considering a Bernoulli process and the probability distribution of $y$ (the number of times the new method fails to detect the disease) is the Binomial:

$$
\text{Binom}(y|n,p) = {n\choose y} p^y(1-p)^{n-y}
$$  

where $n$ is the number of trials and $p$ is the probability of failing to detect the disease.

**(b)** With $n = 75$ and $y = 6$ an unbiased frequentist estimator for the Binomial distribution is

$$
p = \frac{y}{n} = \frac{6}{75} = \frac{2}{25}
$$

**(c)**  If the mean $\mu$ and standard deviation $\sigma$ of the chosen $\text{Beta}(a, b)$ prior are:

$$\mu = \frac{a}{a + b} = 0.15 \qquad \qquad 
\sigma^2 = \frac{a b}{(a + b)^2(a + b + 1)} = 0.14 $$

we can invert this expression and find:
$$
\Longrightarrow a = \mu \left( \frac{\mu (1- \mu)}{\sigma^2} -1 \right) \approx 0.826 \qquad \qquad
b = \left( \frac{\mu (1- \mu)}{\sigma^2} -1 \right)(1 - \mu) \approx 4.679$$ 

Then, since the Beta distribution is the conjugate prior for the Binomial, the Posterior will still be a $\text{Beta}(\bar{a},\bar{b})$ distribution with 

$$\bar{a}= a + y = 0.826 + 6 \approx 6.826 \quad \text{ and } \quad \bar{b}= b + n - y = 4.679 + 75 - 6 \approx 73.68$$

and with mean and variance:

$$\bar{\mu} = \frac{\bar{a}}{\bar{a} + \bar{b}} \approx 0.085 \qquad \qquad 
\bar{\text{Var}} = \frac{\bar{a} \bar{b}}{(\bar{a} + \bar{b})^2(\bar{a} + \bar{b} + 1)} \approx 0.0009 $$

(Calculations below)

```{r}
y <- 6
n <- 75

# Prior parameters
m1 <- 0.15
s1 <- 0.14

a1 <- m1*((m1*(1-m1)/s1**2)-1)
b1 <- (1-m1)*((m1*(1-m1)/s1**2)-1)

# Posterior parameters
a2 <- a1 + y
b2 <- b1 + n - y

m2 <- a2/(a2+b2)
s2 <- sqrt((a2*b2)/((a2+b2+1)*(a2+b2)**2))

cat('Prior: \n-------------------------------\n')
cat('a: ', a1)
cat('\t b: ', b1, '\n')

cat('\n Posterior: \n---------------------------------------------------------------------------------\n')
cat('a: ', a2)
cat('\t b: ', b2)
cat('\t Mean: ', m2)
cat('\t Variance: ', s2**2)
```

We can also plot these results:

```{r}
samp <- 500
p0 <- seq(0, 1, by=1/samp)

prior <- dbeta(p0, a1, b1)
posterior <- dbeta(p0, a2, b2)

df_plot <- data.frame(x = rep(p0,2), 
                      P = c(prior, posterior), 
                      Key = c(rep("Prior", length(p0)), rep("Posterior", length(p0)))
                     )

options(repr.plot.width=7, repr.plot.height=4)

ggplot(df_plot, aes(x=x, y=P, group = Key)) +
            geom_line(aes(color = Key), size = 1) +
            theme_bw(base_size=14)+
            labs(title = "Prior and Posterior distributions", x = "p0", y = "pdf", color = " ")+
            ylim(0,15)+
            xlim(0,0.25)+
            
            #Prior
            #geom_segment(aes(x = m1, y = 0, xend = m1, yend = 3), linetype="longdash", color = "aquamarine4", size=0.8) +
            #geom_text(aes(x=(m1+0.1), label="Prior Mean", y=3), colour="aquamarine4")+

            #geom_vline(xintercept = (m1-s1**2), linetype="dotted", color = "aquamarine3", size=0.8)+
            #geom_vline(xintercept = (m1+s1**2), linetype="dotted", color = "aquamarine3", size=0.8)+

            #Posterior
            geom_segment(aes(x = m2, y = 0, xend = m2, yend = 13), linetype="longdash", color = "firebrick4", size=0.8) +
            geom_segment(aes(x = 0.15, y = 12.5, xend = 0.17, yend = 12.5),
                         linetype="longdash", color = "firebrick4", size=0.8) +   
            geom_text(aes(x=(m2+0.12), label="Posterior Mean", y=12.5), colour="black")+

            geom_vline(xintercept = (m2-s2**2), linetype="dotted", color = "firebrick3", size=0.8)+
            geom_vline(xintercept = (m2+s2**2), linetype="dotted", color = "firebrick3", size=0.8)+
            geom_segment(aes(x = 0.15, y = 11.5, xend = 0.17, yend = 11.5),
                         linetype="dotted", color = "firebrick3", size=0.8) +
            geom_text(aes(x=(m2+0.12), label="Posterior Var", y=11.5), colour="black")


```

**(d)** If p is the probability of failing to the detect the disesease in ill patients, the null hypothesis is 
$$
H_0: \qquad p < 0.15
$$

and the alternative hypothesis:
$$
H_1: \qquad p \geq 0.15
$$

To test $H_0: p < p_0$ vs $H_1: p \geq p_0$ at a level of significance $\alpha = 5 \%$ we integrate the posterior ($\text{Beta}(\bar{a},\bar{b})$) over the region of interest:

$$
P(H_0: p < 0.15| y=6) = \int_0^{0.15} \frac{\Gamma(\bar{a}+\bar{b})}{\Gamma(\bar{a})\Gamma(\bar{b})} p^{\bar{a}-1}(1-p)^{\bar{b}-1} dp
$$



```{r}
p_H0 <- integrate(function(x) {x*dbeta(x, a2, b2)}, 0, 0.15)

cat('The posterior probability of the null hypothesis is:', p_H0$value*100, '% \n')
```

Since the result $7.95 \%$ is higher than $\alpha = 5 \%$ we cannot reject the null hypothesis at this level of significance.


**(e)** In the frequentist approach we still set the same null and alternative hypothesis. The null distribution of the test statistic is:

    Binom(y|n = 75, p=0.15)

Then we have to calculate the p-value $1 - F(y=6)$ where $F(y)$ is the $cdf$. If $\text{p-value} < \alpha$ then the test statistic lies in the rejection region and we cannot accept the null hypothesis at this level of significance. 

We can also use the built-in function `binom.test()` to perform the frequentist hypothesis test. 

```{r}
p.value <- 1- pbinom(y,n,0.15)

cat('The p-value is:', p.value,'\n')

exact.pval <- binom.test(6, 75, 0.15, alternative = "greater")$p.value

cat('Using the built-in punction for the exact binomial test the p-value is:', exact.pval)
```

Since this value is bigger than $\alpha = 0.05$ we cannot reject the null hypothesis. 

We can also visualize the hypothesis test through the following plot:

```{r}
ys <- seq(0,75)
bars <- 1 - pbinom(ys, 75, 0.15)
alpha <- 0.05

df.freq <- data.frame(x = ys, P = bars)

# Plot
options(repr.plot.width=7, repr.plot.height=5)

ggplot(data=df.freq, aes(x=x, y=P, fill=factor(ifelse(x == '6', 'highligthed','normal')))
      )+ 
            geom_bar(stat="identity", width=0.8, color = 'coral4', size = 0.8, alpha = 0.8)+
            geom_hline(yintercept = alpha, linetype="twodash", color = "blue4", size=0.8)+

            geom_text(aes(x=19, label="alpha", y=0.09), colour="blue4")+

            scale_fill_manual(name = " ", values=c("deepskyblue1","lightpink1"))+
            theme_minimal(base_size=14)+
            theme(legend.position = "none")+
            labs(title = "One-side hypothesis test - frequentist approach", x = "y", y = "1 - F(x)")+
            xlim(0,20)

```

We can see that $y=6$ lies in the acceptance region, thus we cannot reject the null hypothesis at this level of significance (as found in the Bayesian test).

<!-- #region -->
## Exercise 2 

Ladislaus Josephovich Bortkiewicz was a Russian economist and statistician. He noted that the Poisson distribution can be very useful in applied statistics when describing low-frequency events in a large population. In a famous example he showed that the number of deaths by horse kick among the Prussian army follows the Poisson distribution.

Considering the following to sets of observations taken over a fixed large time interval in two different corps:

| $y$ death soldiers |  0  |  1  |  2  |  3  |  4  | ≥ 5 |
|--------------------|:---:|:---:|:---:|:---:|:---:|:---:|
| $n_1$ observations | 109 | 65  | 22  | 3   | 1   | 0   |
| $n_2$ obseravtions | 144 | 91  | 32  | 11  | 2   | 0   |


**(a)** Assuming a uniform prior, compute and plot the posterior distribution for $\lambda$, the death rate over the measurement time. Determine the posterior mean, median and variance, and compute the $95 \%$ credibility interval.

**(b)** Assuming now a Jeffreys' prior,

$$ g(\lambda) \propto 1/\sqrt{\lambda} \qquad \text{with} \lambda > 0$$

compute and plot the posterior distribution for $\lambda$, the death rate over the measurement time. Determine the posterior mean, median and variance, and compute the $95 \%$ credibility interval.
<!-- #endregion -->

### Solution

**(a)** To determine the posterior distribution $P(\lambda|\{y_j\})$ for $\lambda$ we can use Bayes theorem

$$
P(\lambda|\{y_j\}) \propto f(\{y_j\}|\lambda) \times g(\lambda)
$$

where $g(\lambda)$ is the Prior distribution, which we are assuming to be uniform  

$$
g(\lambda) = 1 \qquad \forall \lambda>0
$$

and $f(\{y_j\}|\lambda)$ is the Likelihood, which for multiple independent measurments of a Poisson process like in this case is:

$$
f(\{y_j\}|\lambda) =\prod_{j=1}^{n} f(y_j|\lambda)  \propto \lambda^{\sum y_{j}} \times \mathrm{e}^{-(n \lambda)}
$$

This is equivalent to a Gamma distribution function

$$
\operatorname{Gamma}(y | \alpha, N)=k y^{\alpha-1} \mathrm{e}^{-n y} 
\qquad \text{with} \qquad k= \frac{n^{\alpha}}{\Gamma(\alpha)}
$$

where $\alpha = \sum y_j + 1$ and $n$ is the number of trials.

Given all these considerations, the posterior is:
$$
\begin{aligned}
P(\lambda| \{y_j\}) & \propto f(\{y_j\}|\lambda) \times g(\lambda) \\
& \propto \lambda^{\sum y_{j}} \times \mathrm{e}^{-(n \lambda)} \\
& \propto \operatorname{Gamma}(y | \alpha, n) 
\end{aligned}
$$

We can use the build-in R function `dgamma(mu, alpha, n)` to obtain the normalized Posterior distribution for the two datasets.

```{r}
# - n1 observations ---------------------------------------------------------------------------------------------------
alpha1 <- 1 + (65 + 2*22 + 3*3 + 4)
n1 <- 109+65+22+3+1

n.sample <- 3000
lamb <- seq(0,2, length.out = n.sample)

PostU1 <- dgamma(lamb, alpha1, n1)

df1 <- data.frame(lambda = lamb, 
                  Post = PostU1, 
                  key = rep("Set1", length(lamb))
                  )

# - n2 observations ---------------------------------------------------------------------------------------------------
alpha2 <- 1 + (91 + 2*32 + 3*11 + 4*2)
n2 <- 144+91+32+11+2

PostU2 <- dgamma(lamb, alpha2, n2)

df2 <- data.frame(lambda = lamb, 
                  Post = PostU2, 
                  key = rep("Set2", length(lamb))
                  )

dfUnif <- rbind(df1, df2)
```

Now we can compute the posterior mean, median and variance, and compute the $95 \%$  credibility interval. We know that for a `Gamma($\alpha$, $N$)` distribution the analytical expression of the mean and variance are:

$$
E[\lambda|y] = \frac{\alpha}{N} \qquad \text{Var}[\lambda|y] = \frac{\alpha}{N^2}
$$

```{r}
# - n1 observations ---------------------------------------------------------------------------------------------------
mean1 <- alpha1/n1
var1 <- alpha1/(n1*n1)
median1 <- qgamma(0.5, alpha1, n1)

min_CI1 <- qgamma(0.025, alpha1, n1)
max_CI1 <- qgamma(0.975, alpha1, n1)

cat("- Set 1 -----------------")
cat("Mean:", mean1, '\n')
cat("Variance:", var1, '\n')
cat("Median:", median1, '\n')
cat("95% C.I.: [", min_CI1, ',', max_CI1,']\n')

# - n2 observations ---------------------------------------------------------------------------------------------------
mean2 <- alpha2/n2
var2 <- alpha2/(n2*n2)
median2 <- qgamma(0.5, alpha2, n2)

min_CI2 <- qgamma(0.025, alpha2, n2)
max_CI2 <- qgamma(0.975, alpha2, n2)

cat("\n - Set 2 -----------------")
cat("Mean:", mean2, '\n')
cat("Variance:", var2, '\n')
cat("Median:", median2, '\n')
cat("95% C.I.: [", min_CI2, ',', max_CI2,']\n')
```

```{r}
# - Plot ---------------------------------------------------------------------------------------------------
options(repr.plot.width=10, repr.plot.height=5)

plot1 <- ggplot(df1, aes(x=lambda, y=Post)) +
            geom_line(color = 'coral2', size = 1) +
            geom_segment(aes(x = mean1, y = 0, xend = mean1, yend = 7), linetype="longdash", color = "red4", size=0.8)+
            geom_vline(xintercept =  min_CI1, linetype="dotted", color = "red2", size=0.8)+
            geom_vline(xintercept = max_CI1, linetype="dotted", color = "red2", size=0.8)+
            geom_ribbon(data=subset(df1 ,lambda>0 & lambda<min_CI1),aes(ymax=Post),ymin=0,fill="red",colour=NA,alpha=0.6)+
            geom_ribbon(data=subset(df1 ,lambda>max_CI1 & lambda<2),aes(ymax=Post),ymin=0,fill="red",colour=NA,alpha=0.6)+
            
            #Legend
            geom_segment(aes(x = 1, y = 6, xend = 1.2, yend = 6), linetype="longdash", color = "red4", size=0.8)+
            geom_text(aes(x=1.35, label="Mean", y=6), colour="black") +
            geom_segment(aes(x = 1, y = 5, xend = 1.2, yend = 5), linetype="dotted", color = "red2", size=0.8)+
            geom_text(aes(x=1.4, label="95 % C.I.", y=5), colour="black") +

        theme_bw(base_size=14)+
        labs(title = "Set1", x = expression(lambda), y = expression(paste('P(', lambda, '| D)')))+
        ylim(0,8)+xlim(0,2)

plot2 <- ggplot(df2, aes(x=lambda, y=Post)) +
            geom_line(color = 'cyan2', size = 1) +

            geom_segment(aes(x = mean2, y = 0, xend = mean2, yend = 8), linetype="longdash", color = "blue4", size=0.8)+            
            geom_vline(xintercept =  min_CI2, linetype="dotted", color = "blue2", size=0.8)+
            geom_vline(xintercept = max_CI2, linetype="dotted", color = "blue2", size=0.8)+
            geom_ribbon(data=subset(df2,lambda>0 & lambda<min_CI2),aes(ymax=Post),ymin=0,fill="blue",colour=NA,alpha=0.5)+
            geom_ribbon(data=subset(df2,lambda>max_CI2 & lambda<2),aes(ymax=Post),ymin=0,fill="blue",colour=NA,alpha=0.5)+

            #Legend
            geom_segment(aes(x = 1, y = 6, xend = 1.2, yend = 6), linetype="longdash", color = "blue4", size=0.8)+
            geom_text(aes(x=1.35, label="Mean", y=6), colour="black") +
            geom_segment(aes(x = 1, y = 5, xend = 1.2, yend = 5), linetype="dotted", color = "blue2", size=0.8)+
            geom_text(aes(x=1.4, label="95 % C.I.", y=5), colour="black") +

        theme_bw(base_size=14)+
        labs(title = "Set2", x = expression(lambda), y = expression(paste('P(', lambda, '| D)')))+
        ylim(0,8)+xlim(0,2)

tgrob <- text_grob('Posterior distributions using Uniform Prior',size = 18)
plot0 <- as_ggplot(tgrob)

ggarrange(plot0, NULL ,plot1, plot2, ncol = 2,nrow = 2,heights = c(1,5))
```

**(b)** If we instead choose as $g(\lambda)$ Jeffrey's Prior   

$$
g(\lambda) \propto \frac{1}{\sqrt{\lambda}} \qquad \forall \lambda>0
$$

combining it with the Likelihood the Posterior is:

$$
\begin{aligned}
P(\lambda|\{y_j\}) & \propto f(\{y_j\}|\lambda) \times g(\lambda) \\
& \propto \lambda^{\sum y_{j}} \times \mathrm{e}^{-(n \lambda)} \times \frac{1}{\sqrt{\lambda}}\\
& \propto \lambda^{\sum y_{j} - \frac{1}{2}} \times \mathrm{e}^{-(n \lambda)}\\
& \propto \operatorname{Gamma}(y | \alpha', n')
\end{aligned}
$$

where $\alpha' = \sum y_j + 1\frac{1}{2}$ and $n'$ is the number of trials.

We can thus proceed as done with the uniform Prior.

```{r}
# - n1 observations ---------------------------------------------------------------------------------------------------
j.alpha1 <- 1/2 + (65 + 2*22 + 3*3 + 4)

n.sample <- 3000
lamb <- seq(0,2, length.out = n.sample)

PostJ1 <- dgamma(lamb, j.alpha1, n1)

dfj1 <- data.frame(lambda = lamb, 
                  Post = PostJ1, 
                  key = rep("Set1", length(lamb))
                  )

# - n2 observations ---------------------------------------------------------------------------------------------------
j.alpha2 <- 1/2 + (91 + 2*32 + 3*11 + 4*2)

PostJ2 <- dgamma(lamb, j.alpha2, n2)

dfj2 <- data.frame(lambda = lamb, 
                  Post = PostJ2, 
                  key = rep("Set2", length(lamb))
                  )

```

```{r}
# - n1 observations ---------------------------------------------------------------------------------------------------
meanj1 <- j.alpha1/n1
varj1 <- j.alpha1/(n1*n1)
medianj1 <- qgamma(0.5, j.alpha1, n1)

j.min_CI1 <- qgamma(0.025, j.alpha1, n1)
j.max_CI1 <- qgamma(0.975, j.alpha1, n1)

cat("- Set 1 -----------------")
cat("Mean:", meanj1, '\n')
cat("Variance:", varj1, '\n')
cat("Median:", medianj1, '\n')
cat("95% C.I.: [", j.min_CI1, ',', j.max_CI1,']\n')

# - n2 observations ---------------------------------------------------------------------------------------------------
meanj2 <- j.alpha2/n2
varj2 <- j.alpha2/(n2*n2)
medianj2 <- qgamma(0.5, j.alpha2, n2)

j.min_CI2 <- qgamma(0.025, j.alpha2, n2)
j.max_CI2 <- qgamma(0.975, j.alpha2, n2)

cat("\n - Set 2 -----------------")
cat("Mean:", meanj2, '\n')
cat("Variance:", varj2, '\n')
cat("Median:", medianj2, '\n')
cat("95% C.I.: [", j.min_CI2, ',', j.max_CI2,']\n')
```

```{r}
# - Plot ---------------------------------------------------------------------------------------------------
options(repr.plot.width=10, repr.plot.height=5)

plotj1 <- ggplot(dfj1, aes(x=lambda, y=Post)) +
            geom_line(color = 'mediumorchid2', size = 1) +
            geom_segment(aes(x = meanj1, y = 0, xend = meanj1, yend = 7), linetype="longdash", color = "purple4", size=0.8)+
            geom_vline(xintercept = j.min_CI1, linetype="dotted", color = "purple2", size=0.8)+
            geom_vline(xintercept = j.max_CI1, linetype="dotted", color = "purple2", size=0.8)+
            geom_ribbon(data=subset(dfj1 ,lambda>0 & lambda<j.min_CI1),aes(ymax=Post),ymin=0,fill="purple",colour=NA,alpha=0.6)+
            geom_ribbon(data=subset(dfj1 ,lambda>max_CI1 & lambda<2),aes(ymax=Post),ymin=0,fill="purple",colour=NA,alpha=0.6)+
            
            #Legend
            geom_segment(aes(x = 1, y = 6, xend = 1.2, yend = 6), linetype="longdash", color = "purple4", size=0.8)+
            geom_text(aes(x=1.35, label="Mean", y=6), colour="black") +
            geom_segment(aes(x = 1, y = 5, xend = 1.2, yend = 5), linetype="dotted", color = "purple2", size=0.8)+
            geom_text(aes(x=1.4, label="95 % C.I.", y=5), colour="black") +

        theme_bw(base_size=14)+
        labs(title = "Set1", x = expression(lambda), y = expression(paste('P(', lambda, '| D)')))+
        ylim(0,8)+xlim(0,2)

plotj2 <- ggplot(dfj2, aes(x=lambda, y=Post)) +
            geom_line(color = 'springgreen2', size = 1) +

            geom_segment(aes(x = meanj2, y = 0, xend = meanj2, yend = 8), linetype="longdash", color = "green4", size=0.8)+            
            geom_vline(xintercept = j.min_CI2, linetype="dotted", color = "green2", size=0.8)+
            geom_vline(xintercept = j.max_CI2, linetype="dotted", color = "green2", size=0.8)+
            geom_ribbon(data=subset(dfj2,lambda>0 & lambda<j.min_CI2),aes(ymax=Post),ymin=0,fill="green",colour=NA,alpha=0.4)+
            geom_ribbon(data=subset(dfj2,lambda>j.max_CI2 & lambda<2),aes(ymax=Post),ymin=0,fill="green",colour=NA,alpha=0.4)+

            #Legend
            geom_segment(aes(x = 1, y = 6, xend = 1.2, yend = 6), linetype="longdash", color = "green4", size=0.8)+
            geom_text(aes(x=1.35, label="Mean", y=6), colour="black") +
            geom_segment(aes(x = 1, y = 5, xend = 1.2, yend = 5), linetype="dotted", color = "green2", size=0.8)+
            geom_text(aes(x=1.4, label="95 % C.I.", y=5), colour="black") +

        theme_bw(base_size=14)+
        labs(title = "Set2", x = expression(lambda), y = expression(paste('P(', lambda, '| D)')))+
        ylim(0,8)+xlim(0,2)

tgrob <- text_grob('Posterior distributions using Jeffrey\'s Prior',size = 18)
plot0 <- as_ggplot(tgrob)

ggarrange(plot0, NULL ,plotj1, plotj2, ncol = 2,nrow = 2,heights = c(1,5))
```

The results are not very influenced by the choice of the Prior distribution.


## Exercise 3

* A study on water quality of streams, a high level of bacter X was defined as a level greater than 100 per 100 mL of stream water. $n = 116$ samples were taken from streams having a high environmental impact on pandas. Out of these, $y = 11$ had a high bacter X level.

* Indicating with $p$ the probability that a sample of water taken from the stream has a high bacter X level,

**(a)** Find the frequentist estimator for $p$

**(b)** Using a Beta(1; 10) prior for $p$, calculate and posterior distribution $P(p|y)$

**(c)** Find the bayesian estimator for p, the posterior mean and variance, and a $95 \%$ credible interval

**(d)** Test the hypotesis
$$H_0 : p = 0.1 \qquad \text{versus} \qquad H_1: p \neq 0.1$$
at $5 \%$ level of significance with both the frequentist and bayesian approach

* A new measurement, performed one month later on $n = 165$ water samples, gives $y = 9$ high bacter X level

**(e)** Find the frequentist estimator for $p$

**(f)** Find a bayesian estimator for $p$, assuming both a Beta(1; 10) prior for $p$, and assuming the posterior probability of the older measurement as the prior for the new one.

**(g)** Find the bayesian estimator for p, the posterior mean and variance, and a $95 \%$ credible interval

**(h)** Test the hypotesis
$$H_0 : p = 0.1 \qquad \text{versus} \qquad H_1: p \neq 0.1$$
at $5 \%$ level of significance with both the frequentist and bayesian approach.


### Solution

**(a)** Since the result of the test on the quality of the water can only have two possible results (high or low) we are considering a Bernoulli process and the probability distribution of $y$ (the number of times that a sample of water taken from the stream has a high bacter X level) is Binomial. Thus, an unbiased frequentist estimator for $p_F$ is:

$$
p_F = \frac{y}{n} = \frac{11}{116} \approx 0.0948
$$

where $n$ is the number of trials.

**(b)** By assuming as Prior $\text{Beta}(1, 10)$, since the Beta distribution is the conjugate prior for the Binomial, the Posterior will still be a $\text{Beta}(\bar{a},\bar{b})$ distribution with 

$$\bar{a}= a + y = 1 + 11 = 12 \quad \text{ and } \quad \bar{b}= b + n - y = 10 + 116 -11 = 115$$


**(c)**  The bayesian estimator for $p$ is the Posterior mean. 

The Posterior has mean and variance:

$$\bar{\mu} = \frac{\bar{a}}{\bar{a} + \bar{b}} \approx 0.0945 \qquad \qquad 
\bar{\text{Var}} = \frac{\bar{a} \bar{b}}{(\bar{a} + \bar{b})^2(\bar{a} + \bar{b} + 1)} \approx 0.00067 $$

Thus:
$$
p_B = \frac{\bar{a}}{\bar{a} + \bar{b}} \approx 0.0945
$$

We can compute the posterior mean and variance and a 95%  credible interval as below.

```{r}
y <- 11
n <- 116

# Prior parameters
a1 <- 1
b1 <- 10

# Posterior parameters
a2 <- a1 + y
b2 <- b1 + n - y

m2 <- a2/(a2+b2)
s2 <- sqrt((a2*b2)/((a2+b2+1)*(a2+b2)**2))

min_CI <- qbeta(0.025, a2, b2)
max_CI <- qbeta(0.975, a2, b2)

cat('\n Prior: \n-------------------------------')
cat('\n a: ', a1)
cat('\t b: ', b1, '\n')

cat('\n Posterior: \n---------------------------------------------------------------------------------')
cat('\n a: ', a2)
cat('\n b: ', b2)
cat('\n Mean: ', m2)
cat('\n Variance: ', s2**2)
cat('\n 95% C.I.: [', min_CI, ',', max_CI,']\n')

samp <- 500
p0 <- seq(0, 1, by=1/samp)

prior <- dbeta(p0, a1, b1)
posterior <- dbeta(p0, a2, b2)

df_plot2 <- data.frame(x = rep(p0,2), 
                      P = c(prior, posterior), 
                      Key = c(rep("Prior", length(p0)), rep("Posterior", length(p0)))
                     )

```

```{r}
options(repr.plot.width=7, repr.plot.height=4)

ggplot(df_plot2, aes(x=x, y=P, group = Key)) +
            geom_line(aes(color = Key), size = 1) +
            theme_bw(base_size=14)+
            labs(title = "Prior and Posterior distributions", x = "p0", y = "pdf", color = " ")+
            ylim(0,16)+
            xlim(0,0.5)+

            #Posterior
            geom_segment(aes(x = m2, y = 0, xend = m2, yend = 15.5), linetype="longdash", color = "firebrick4", size=0.8) +
            geom_segment(aes(x = 0.3, y = 12.5, xend = 0.35, yend = 12.5),
                         linetype="longdash", color = "firebrick4", size=0.8) +   
            geom_text(aes(x=0.42, label="Posterior Mean", y=12.5), colour="black")+

            geom_vline(xintercept = min_CI, linetype="dotted", color = "firebrick3", size=0.8)+
            geom_vline(xintercept = max_CI, linetype="dotted", color = "firebrick3", size=0.8)+
            geom_segment(aes(x = 0.3, y = 11.5, xend = 0.35, yend = 11.5),
                         linetype="dotted", color = "firebrick3", size=0.8) +
            geom_text(aes(x=0.4, label="95% C.I.", y=11.5), colour="black")
```

**(d)** We now want to perform an hypotesis test at $5 \%$ level of significance with both the frequentist and bayesian approach where the null hypothesis is:

$$H_0 : p = 0.1 $$

and the alternative hypothesis is:

$$H_1: p \neq 0.1$$

Let's start with the **Frequentist approach**.

The null distribution of the test statistic is:

    Binom(y|n = 116, p=0.1)
    
To estimate the rejection interval we can use the quantile function in a symmetric way to find the two extremes of the rejection area corresponding to a value of $\alpha$ as close as possible to $5\%$. 
    
    left <- qbinom(0.025, n, 0.1)
    right <- qbinom(0.975, n, 0.1)

Then we can then refine our choice of the left and right extremes of the rejection region by selecting two values yielding a level of significance as close as possible to $\alpha$.

```{r}
left <- qbinom(0.025, n, 0.1)
right <- qbinom(0.975, n, 0.1)

y.l <- pbinom(left, n, 0.1)
y.r <- 1- pbinom(right, n, 0.1)

cat('With', left, 'as left extreme and', right, 'as right one we get alpha =', y.l+y.r, '\n')

y.l <- pbinom(left, n, 0.1)
y.r <- 1- pbinom(right+1, n, 0.1)

cat('With', left, 'as left extreme and', right+1, 'as right one we get alpha =', y.l+y.r, '\n')

y.l <- pbinom(left-1, n, 0.1)
y.r <- 1- pbinom(right, n, 0.1)

cat('With', left-1, 'as left extreme and', right, 'as right one we get alpha =', y.l+y.r)
```

The best choice is to select as rejection region $[0,5] \cup [18,110]$. We can see that $y = 11$ lies in the acceptance rejon. Thus we cannot reject the null hypothesis at this level of significance.

Then we have to calculate the p-value $1 - F(y=6)$ where $F(y)$ is the $cdf$. If $\text{p-value} < \alpha$ then the test statistic lies in the rejection region and we cannot accept the null hypothesis at this level of significance as shown in the following plot.

```{r}
pleft <- dbinom(left-1, 116, 0.1)
pright <- dbinom(right, 116, 0.1)

rej.level <- pright

ys <- seq(0,116)
bars <- dbinom(ys, 116, 0.1)
accept <- c(rep(0, 6), rep(1, right-left), rep(0, n-right+1))

df.freq2 <- data.frame(x = ys, P = bars, acc = accept)
```

```{r}
# Plot
options(repr.plot.width=7, repr.plot.height=5)

ggplot(data=df.freq2, aes(x=x, y=P, fill=factor(ifelse(acc == '1', 'Accept','Reject')))
      )+ 
            geom_bar(stat="identity", width=0.8, color = 'coral4', size = 0.8, alpha = 0.8)+
            geom_hline(yintercept = rej.level, linetype="twodash", color = "blue4", size=0.8)+

            scale_fill_manual(name = " ", values=c("deepskyblue1","lightpink1"))+
            theme_minimal(base_size=14)+
            labs(title = "Two-sides hypothesis test - frequentist approach", x = "y", y = "pdf")+
            xlim(0,25)

```

Let's now repeat the same analysis in the **Bayesian approach**.

In this case to test $H_0$ vs $H_1$ at a level of significance $\alpha = 5 \%$, since the probability of an exact value like the null hypothesis is zero we need to use credibility intervals:

* We compute a $(1- \alpha)\times 100 \% = 95 \%$ credible interval for p
* If $p_0 = 0.10$ lies outside the interval we reject the null hypothesis. 

We already found in the previous point that a $95 \%$ credible interval for our Posterior distribution is: $\approx [ 0.05, 0.15]$. Since $p_0 = 0.1$ lies inside this interval we cannot reject the null hypothesis at this level of significance.

```{r}
df_post <- data.frame(x = p0, P = posterior)
p.rej <- 0.1

options(repr.plot.width=7, repr.plot.height=4)

ggplot(df_post, aes(x=x, y=P)) +
            geom_line(color = 'coral4', size = 1) +
            theme_bw(base_size=14)+
            labs(title = "Two-sides hypothesis test - Bayesian approach", x = "p0", y = "pdf", color = " ")+
            ylim(0,16)+
            xlim(0,0.5)+

            geom_segment(aes(x = p.rej, y = 0, xend = p.rej, yend = 14.5), linetype="solid", color = "blue4", size=0.8) +
            geom_segment(aes(x = 0.2, y = 12.5, xend = 0.22, yend = 12.5),
                         linetype="solid", color = "blue4", size=0.8) +   
            geom_text(aes(x=0.25, label="p0 = 0.10", y=12.5), colour="black")+

            geom_vline(xintercept = min_CI, linetype="dotted", color = "firebrick3", size=0.8)+
            geom_vline(xintercept = max_CI, linetype="dotted", color = "firebrick3", size=0.8)+

            #Reject region
            geom_ribbon(data=subset(df_post,x>0 & x<=min_CI),aes(ymax=P),ymin=0,fill="red",colour=NA,alpha=0.4)+
            geom_ribbon(data=subset(df_post,x>=max_CI & x<1),aes(ymax=P),ymin=0,fill="red",colour=NA,alpha=0.4)+

            # Accept region
            geom_ribbon(data=subset(df_post,x>=min_CI & x<=max_CI),aes(ymax=P),ymin=0,fill="cyan",colour=NA,alpha=0.2)+

            geom_segment(aes(x = 0.2, y = 11.5, xend = 0.22, yend = 11.5),
                         linetype="dotted", color = "firebrick3", size=0.8) +
            geom_text(aes(x=0.25, label="95% C.I.", y=11.5), colour="black")
```

**(e)**  A new measurement, performed one month later on $n = 165$ water samples, gives $y = 9$ high bacter X level. We repeat the same analysis also in this case.

As before, an unbiased frequentist estimator for $p_F$ is:

$$
p_F = \frac{y}{n} = \frac{9}{165} \approx 0.054
$$


**(f)** By assuming as Prior $\text{Beta}(1, 10)$ as in point **(b)** the Posterior will still be a $\text{Beta}(a',b')$ distribution with 

$$a'= a + y = 1 + 9 = 10 \quad \text{ and } \quad b' = b + n - y = 10 + 165 - 9 = 166$$

On the other hand by choosing as Prior the previous Posterior $\text{Beta}(\bar{a}, \bar{b}) = \text{Beta}(12,115)$ the Posterior will, again, be a $\text{Beta}(a'',b'')$ distribution with 

$$a''= \bar{a} + y = 12 + 9 = 21 \quad \text{ and } \quad b'' = \bar{b} + n - y = 115 + 165 - 9 = 271 $$


**(g)** Again, the bayesian estimator for $p$ is the Posterior mean. 
We can calculate all the relevant quantities as before:

```{r}
y <- 9
n <- 165

# - With Beta(1,10) prior ----------------------------------------------------------------------------------------------
# Prior1 parameters
a.pr1 <- 1
b.pr1 <- 10

# Posterior1 parameters
a.pos1 <- a.pr1 + y
b.pos1 <- b.pr1 + n - y

m.1 <- a.pos1/(a.pos1+b.pos1)
s.1 <- sqrt((a.pos1*b.pos1)/((a.pos1 + b.pos1 +1)*(a.pos1 + b.pos1)**2))

min_CI1 <- qbeta(0.025, a.pos1, b.pos1)
max_CI1 <- qbeta(0.975, a.pos1, b.pos1)


cat('--------------------------------------------------')
cat('\n Prior:')
cat('\n a: ', a.pr1)
cat('\t b: ', b.pr1, '\n')

cat('\n Posterior:')
cat('\n a\': ', a.pos1)
cat('\n b\': ', b.pos1)
cat('\n Mean: ', m.1)
cat('\n Variance: ', s.1**2)
cat('\n 95% C.I.: [', min_CI1, ',', max_CI1,']\n')
cat('--------------------------------------------------')

# - With Previous Posterior as prior ---------------------------------------------------------------------------------
# Prior1 parameters
a.pr2 <- a2
b.pr2 <- b2

# Posterior1 parameters
a.pos2 <- a.pr2 + y
b.pos2 <- b.pr2 + n - y

m.2 <- a.pos2/(a.pos2+b.pos2)
s.2 <- sqrt((a.pos2*b.pos2)/((a.pos2 + b.pos2 +1)*(a.pos2 + b.pos2)**2))

min_CI2 <- qbeta(0.025, a.pos2, b.pos2)
max_CI2 <- qbeta(0.975, a.pos2, b.pos2)


cat('--------------------------------------------------')
cat('\n Prior:')
cat('\n a: ', a.pr2)
cat('\t b: ', b.pr2, '\n')

cat('\n Posterior:')
cat('\n a\'\': ', a.pos2)
cat('\n b\'\': ', b.pos2)
cat('\n Mean: ', m.2)
cat('\n Variance: ', s.2**2)
cat('\n 95% C.I.: [', min_CI2, ',', max_CI2,']\n')
cat('--------------------------------------------------')
```

```{r}
samp <- 500
p0 <- seq(0, 1, by=1/samp)

# - With Beta(1,10) prior ----------------------------------------------------------------------------------------------
prior1 <- dbeta(p0, a.pr1, b.pr1)
posterior1 <- dbeta(p0, a.pos1, b.pos1)

df1_plot <- data.frame(x = rep(p0,2), 
                      P = c(prior1, posterior1), 
                      Key = c(rep("Prior", length(p0)), rep("Posterior", length(p0)))
                     )

# - With Previous Posterior as prior ---------------------------------------------------------------------------------
prior2 <- dbeta(p0, a.pr2, b.pr2)
posterior2 <- dbeta(p0, a.pos2, b.pos2)

df2_plot <- data.frame(x = rep(p0,2), 
                      P = c(prior2, posterior2), 
                      Key = c(rep("Prior", length(p0)), rep("Posterior", length(p0)))
                     )
```

```{r}
# - Plot -----------------------------------------------------------------

options(repr.plot.width=10, repr.plot.height=5)

p1 <- ggplot(df1_plot, aes(x=x, y=P, group = Key)) +
            geom_line(aes(color = Key), size = 1) +
            theme_bw(base_size=14)+
            labs(title = "With Beta(1, 10) Prior", x = "p0", y = "pdf", color = " ")+
            ylim(0,25)+
            xlim(0,0.5)+
            geom_segment(aes(x = m.1, y = 0, xend = m.1, yend = 23), linetype="longdash", color = "firebrick4", size=0.8) +
            geom_segment(aes(x = 0.3, y = 14.5, xend = 0.35, yend = 14.5),
                         linetype="longdash", color = "firebrick4", size=0.8) +   
            geom_text(aes(x=0.38, label="Mean", y=14.5), colour="black")+

            geom_vline(xintercept = min_CI1, linetype="dotted", color = "firebrick3", size=0.8)+
            geom_vline(xintercept = max_CI1, linetype="dotted", color = "firebrick3", size=0.8)+
            geom_segment(aes(x = 0.3, y = 12.5, xend = 0.35, yend = 12.5),
                         linetype="dotted", color = "firebrick3", size=0.8) +
            geom_text(aes(x=0.4, label="95% C.I.", y=12.5), colour="black")+
            theme(legend.position = "none")


p2 <-  ggplot(df2_plot, aes(x=x, y=P, group = Key)) +
            geom_line(aes(color = Key), size = 1) +
            theme_bw(base_size=14)+
            labs(title = "With Beta(12, 115) Prior", x = "p0", y = "pdf", color = " ")+
            ylim(0,30)+
            xlim(0,0.5)+
            geom_segment(aes(x = m.2, y = 0, xend = m.2, yend = 27), linetype="longdash", color = "firebrick4", size=0.8) +
            geom_segment(aes(x = 0.3, y = 17, xend = 0.35, yend = 17),
                         linetype="longdash", color = "firebrick4", size=0.8) +   
            geom_text(aes(x=0.38, label="Mean", y=17), colour="black")+

            geom_vline(xintercept = min_CI2, linetype="dotted", color = "firebrick3", size=0.8)+
            geom_vline(xintercept = max_CI2, linetype="dotted", color = "firebrick3", size=0.8)+
            geom_segment(aes(x = 0.3, y = 15, xend = 0.35, yend = 15),
                         linetype="dotted", color = "firebrick3", size=0.8) +
            geom_text(aes(x=0.4, label="95% C.I.", y=15), colour="black")


tgrob <- text_grob('Posterior distributions',size = 18)
plot0 <- as_ggplot(tgrob)

ggarrange(plot0, NULL ,p1, p2, ncol = 2,nrow = 2, widths = c(4,5), heights = c(1,5))
```

**(h)** We now repeat the previous hypothesis test at $5 \%$ level of significance with both the frequentist and bayesian approach.

Let's start with the **Frequentist approach**.

```{r}
left <- qbinom(0.025, n, 0.1)
right <- qbinom(0.975, n, 0.1)

y.l <- pbinom(left, n, 0.1)
y.r <- 1- pbinom(right, n, 0.1)

cat('With', left, 'as left extreme and', right, 'as right one we get alpha =', y.l+y.r, '\n')

y.l <- pbinom(left, n, 0.1)
y.r <- 1- pbinom(right+1, n, 0.1)

cat('With', left, 'as left extreme and', right+1, 'as right one we get alpha =', y.l+y.r, '\n')

pleft <- dbinom(left-1, 165, 0.1)
pright <- dbinom(right, 165, 0.1)

rej.level <- pleft

ys <- seq(0,165)
bars <- dbinom(ys, 165, 0.1)
accept <- c(rep(0, 9), rep(1, right-left), rep(0, n-right+1))

df.freq2 <- data.frame(x = ys, P = bars, acc = accept)

# Plot
options(repr.plot.width=7, repr.plot.height=5)

ggplot(data=df.freq2, aes(x=x, y=P, fill=factor(ifelse(acc == '1', 'Accept','Reject')))
      )+ 
            geom_bar(stat="identity", width=0.8, color = 'coral4', size = 0.8, alpha = 0.8)+
            geom_hline(yintercept = rej.level, linetype="twodash", color = "blue4", size=0.8)+

            scale_fill_manual(name = " ", values=c("deepskyblue1","lightpink1"))+
            theme_minimal(base_size=14)+
            labs(title = "Two-sides hypothesis test - frequentist approach", x = "y", y = "pdf")+
            xlim(0,35)
```

We can see that $y=9$ is in the acceptance region (although just at the border), thus we cannot reject $H_0$ at this level of significance.

Let's now repeat the same analysis in the **Bayesian approach** for both the posteriors we obtained before.

```{r}
df_post1 <- data.frame(x = p0, P = posterior1)
df_post2 <- data.frame(x = p0, P = posterior2)
p.rej <- 0.1

options(repr.plot.width=7, repr.plot.height=4)

p1 <- ggplot(df_post1, aes(x=x, y=P)) +
            geom_line(color = 'coral4', size = 1) +
            theme_bw(base_size=12)+
            labs(title = "With Beta(1, 10) Prior", x = "p0", y = "pdf", color = " ")+
            ylim(0,25)+
            xlim(0,0.15)+

            geom_vline(xintercept = p.rej, linetype="solid", color = "blue4", size=0.8) +
            geom_segment(aes(x = 0.2, y = 17, xend = 0.25, yend = 17),
                         linetype="solid", color = "blue4", size=0.8) +   
            geom_text(aes(x=0.12, label="p0 = 0.10", y=17), colour="blue4")+

            geom_vline(xintercept = min_CI1, linetype="dotted", color = "firebrick3", size=1)+
            geom_vline(xintercept = max_CI1, linetype="dotted", color = "firebrick3", size=1)+

            #Reject region
            geom_ribbon(data=subset(df_post1,x>0 & x<=min_CI1),aes(ymax=P),ymin=0,fill="red",colour=NA,alpha=0.4)+
            geom_ribbon(data=subset(df_post1,x>=max_CI1 & x<1),aes(ymax=P),ymin=0,fill="red",colour=NA,alpha=0.4)+

            # Accept region
            geom_ribbon(data=subset(df_post1,x>=min_CI1 & x<=max_CI1),aes(ymax=P),ymin=0,fill="cyan",colour=NA,alpha=0.2)


p2 <- ggplot(df_post2, aes(x=x, y=P)) +
            geom_line(color = 'coral4', size = 1) +
            theme_bw(base_size=12)+
            labs(title = "With Beta(12, 115) Prior", x = "p0", y = "pdf", color = " ")+
            ylim(0,30)+
            xlim(0,0.15)+

            geom_vline(xintercept = p.rej, linetype="solid", color = "blue4", size=0.8) +
            geom_segment(aes(x = 0.2, y = 12.5, xend = 0.22, yend = 12.5),
                         linetype="solid", color = "blue4", size=0.8) +   
            geom_text(aes(x=0.12, label="p0 = 0.10", y=20), colour="blue4")+

            geom_vline(xintercept = min_CI2, linetype="dotted", color = "firebrick3", size=1)+
            geom_vline(xintercept = max_CI2, linetype="dotted", color = "firebrick3", size=1)+

            #Reject region
            geom_ribbon(data=subset(df_post2,x>0 & x<=min_CI2),aes(ymax=P),ymin=0,fill="red",colour=NA,alpha=0.4)+
            geom_ribbon(data=subset(df_post2,x>=max_CI2 & x<1),aes(ymax=P),ymin=0,fill="red",colour=NA,alpha=0.4)+

            # Accept region
            geom_ribbon(data=subset(df_post2,x>=min_CI2 & x<=max_CI2),aes(ymax=P),ymin=0,fill="cyan",colour=NA,alpha=0.2)


tgrob <- text_grob('Bayesian approach',size = 16)
plot0 <- as_ggplot(tgrob)

ggarrange(plot0, NULL ,p1, p2, ncol = 2,nrow = 2, heights = c(1,5))
```

Using the previously computed C.I. for the two Posteriors, we can see that when using as Prior $\text{Beta}(1,10)$  $p_0$ lies outside the C.I. $[0.0277, 0.0954]$ so we can reject the null hypothesis at this level of significance.

The same cannot be said when using $\text{Beta}(12,115)$ as Prior as in this case $p_0$ is in the C.I. $[ 0.0452, 0.1041]$ and so we cannot reject the null hypothesis.

```{r}

```

```{r}

```
