---
jupyter:
  jupytext:
    text_representation:
      extension: .Rmd
      format_name: rmarkdown
      format_version: '1.2'
      jupytext_version: 1.10.3
  kernelspec:
    display_name: R
    language: R
    name: ir
---

# R lab exercises - Set 1

```{r}
# ** Libraries and packages **
#install.packages("ggthemes")
#install.packages("ggpubr")
    library(tidyverse)
    library(repr)
    library(ggthemes)
    library("ggpubr")
    library(scales)
    library(lubridate)  
    library(reshape2)
```

## Exercise 1 - vectors and dataframes

The following table gives the volume, area, length and maximum and mean depths of some Scottish lakes. 
Create vectors, holding the lake's name and all the parameters and build a dataframe called `scottish.lakes` from the vectors

1. Evaluate the highest and lowest volume and area lake
2. Order the frame with respect to the area and determine the two largest area lakes
3. By summing up the areas occpupied by the lakes, determine the area of Scotland covered by water


### Solution

To begin with, let's create the dataframe containing all the data.

```{r}
Loch <- c('Loch Ness','Loch Lomond','Loch Morar','Loch Tay','Loch Awe',
           'Loch Maree','Loch Ericht','Loch Lochy','Loch Rannoch',
           'Loch Shiel','Loch Katrine','Loch Arkaig','Loch Shin')
Volume <- c(7.45, 2.6, 2.3, 1.6, 1.2, 1.09, 1.08, 1.07, 0.97, 0.79, 0.77, 0.75, 0.35)
Area <- c(56, 71, 27, 26.4, 39, 28.6, 18.6, 16, 19, 19.5, 12.4, 16, 22.5)
Length <- c(39, 36, 18.8, 23, 41, 20, 23, 16, 15.7, 28, 12.9, 19.3, 27.8)
Max_depth <- c(230, 190, 310, 150, 94, 114, 156, 162, 134, 128, 151, 109, 49)
Mean_depth <- c(132, 37, 87, 60.6, 32, 38, 57.6, 70, 51, 40, 43.4, 46.5, 15.5)

scottish.lakes <- data.frame(Loch, Volume, Area, Length, Max_depth, Mean_depth)
scottish.lakes
```

**1.** To find which lakes have the highest and lowest volumes and areas, one can use the functions `which.max()` and `which.min()` to find the index of the lakes with the maximum or minimum value in the `Volume` and `Area` columns.

The result show that **Loch Ness** has the **highest volume**, **Loch Shin** the **lowest**. Moreover **Loch Lomond** has the **largest area** and **Loch Katrine** the **lowest**.

```{r}
scottish.lakes[which.max(scottish.lakes$Volume),] # Lake with highest volume
scottish.lakes[which.min(scottish.lakes$Volume),] # Lake with lowest volume
scottish.lakes[which.max(scottish.lakes$Area),]   # Lake with highest area
scottish.lakes[which.min(scottish.lakes$Area),]   # Lake with lowest area
```

**2.** To order the dataframe by area one can use the function `order()` on the column `Area`. In this way, the first two rows of the ordered dataframe correspond to the lakes with the largest area. These lakes are **Loch Lomond** and **Loch Ness**.

```{r}
scottish.lakes[order(Area, decreasing = TRUE),]       # to sort by area
scottish.lakes[order(Area, decreasing = TRUE),][1:2,] # to select only the first two lakes
```

**3.** Finally, using the function `sum()` on the column `Area` one can determine the total area of Scotland occupied by lakes which is 372 $m^2$

```{r}
sum(scottish.lakes$Area)
```

## Exercise 2 - Crude Oil Production

The following CSV file
https://drive.google.com/file/d/1cUQ8d0kDOw2lmzMAHIPglpdcnHy4GgF3/view contains data on crude oil prices from 1861 to 2019, measured in US dollars per barrel.

1. Write R code that is able to read the file and import it in a data frame structure. (Hint: before loading the file, open it with a text editor and check its structure);
2. Produce a plot with the Oil price as a function of the year; 
3. Which is the highest price in history? When did it occur?
3. Plot the derivative of the curve, simply evaluated with the finite difference formula (forward derivative):

\begin{equation}
\frac{\partial \text{price}}{\partial \text{year}} = \text{price}_{j+1} -\text{price}_{j}
\end{equation}


### Solution

**1.** To import the file we use the `read.csv()` function, skipping the first row which only contains a "global header" for the whole dataset.

```{r}
data <- read.csv("crude-oil-prices.csv", skip=1, header = TRUE)
oil <- data.frame(data)

str(oil)
head(oil)
```

**2.** Now we can plot the Oil price as a function of the year using `ggplot2`.

```{r}
options(repr.plot.width=6, repr.plot.height=4)

ggplot(oil, aes(x = Year, y = OilPrice)) +
    geom_point(size = 0.8, color = 'darkblue') +
    geom_line(color = 'blue', size = 0.5) +
    labs(title="Crude Oil Prices", subtitle='Global crude oil prices, measured in US dollars per barrel') +
    theme_hc() + 
    scale_x_continuous(name="Year", breaks=seq(1860,2020, 20)) +
    scale_y_continuous(name="Price per barrel [US $]", breaks=seq(0,100,20)) +
    theme(aspect.ratio=9/16)
```

**3.** To find the highest price we can proceed in the same way as in Exercise 1. We find that the highest price was **111.6697 $** and occurred in **2012**.

```{r}
oil[which.max(oil$OilPrice),] 
```

**4.** The derivative of the curve can be computed with the finite difference method using the function `diff()` on the column `OilPrice`. The result will have one less element with respect to the previous columns so to insert it in the dataframe using `mutate()` we must add a `NA` at the end, corresponding to year 2019.

```{r}
# Compute derivative and add to plot
oil <-mutate(oil, Deriv = c(diff(oil[, 'OilPrice']), NA))
```

```{r}
#Plot
options(repr.plot.width=6, repr.plot.height=4)
ggplot(oil, aes(x = Year, y = Deriv)) +
    geom_point(size = 0.8, color = 'darkblue') +
    geom_line(color = 'blue', size = 0.5) +
    labs(title="Derivative of Crude Oil Prices", subtitle='Increment of crude oil prices in US dollars per barrel per year') +
    theme_hc() + 
    scale_x_continuous(name="Year", breaks=seq(1860,2020,20)) +
    scale_y_continuous(name="Derivative of rice per barrel [US$/year]", breaks=seq(-50,50,10)) +
    theme(aspect.ratio=9/16)
```

## Exercise 3 - World Coal Production

The following CSV file https://drive.google.com/file/d/10kgRQGKEC81QoVW9kj8goNzzyLcT0xld/view contains data on the coal production (in TW$\cdot$hour) for several countries in the World.

1. Write R code that is able to read the file and import it in a tibble structure
2. Count the number of countries available in the file and produce a barplot with the number of entries for each country 

For the following items select only the years $\geq$ 1970:

3. Selecting only the year after 1970, determine the total integrated production for each country and print the top 5 Countries with highest coal productions
4. For the 5 top Countries, create a plot of production as a function of time
5. Generate a plot with the cumulative sum of the World's coal production over the years


### Solution

**1.** An is the previous exercise, we import the file using the `read.csv()` function. This time we save the data in a tibble instead of a dataframe.

```{r}
data2 <- read.csv("coal-production-by-country.csv", header = TRUE)
coal <- tibble(data2)

str(coal)
head(coal)
```

**2.** To count the number of countries we must first remove from the tibble the entries related to international aggregates and not to single countries. We then remove them using `filter()`. Then with the function `unique()` on the column `Entity` we can select the unique values, and using `length()` we can see the number of unique elements in the column `Entity`. The number of counties listed is **182**. 

```{r}
not_count <- c('Africa','Asia and Oceania','Asia Pacific','Central and South America','CIS','EU-28',
             'Eurasia','Europe (other)','Europe','North America','OECD','OPEC','Other Africa','Other Asia & Pacific',
             'Other CIS', 'Other S. & Cent. America', 'South & Central America', 'World') 

coal2 <- filter(coal, !(Entity %in% not_count))

length(unique(coal2$Entity))
```

Now we can make the barplot.

```{r}
options(repr.plot.width=6, repr.plot.height=28)

ggplot(coal2, aes(x=Entity)) +
    geom_bar(color="darkslategray2", fill="darkslategray4")+
    coord_flip()+
    geom_text(stat = 'count', aes(label=..count..), hjust=1.3, color="darkslategray2", size=2.5)+
    theme_minimal()

```

**3.** Now we can remove the entries related to years before 1970 with `filter()` and sum the coal production by country using `sum()` on the column `Coal.production..TWh.` grouping data by `Entity` with `group_by`. 

Then, using `arrange()` we can order the entries in descending order and select only the first 5 rows. We find that the top 5 countries with highest coal productions are **China**, **United States**, **Russia**, **Australia** and **India**.

```{r}
filt_coal <- filter(coal2, Year>= 1970) # Select entries only after 1970

total.coal <- filt_coal %>% group_by(Entity) %>% summarise(Total.production..TWh = sum(Coal.production..TWh.)) # Sum by entry
ord.coal <- total.coal %>% arrange(desc(Total.production..TWh)) # Order in descending order

ord.coal[1:5,] # First 5 rows
```

**4.** Using `ggplot2` let's plot the evolution of coal production throughout the years in these 5 countries (after year 1970). To do that, we create a new filtered tibble called `top5` in which only the entries of the top 5 producers are kept. Then we plot it with color by `Entity`.

```{r}
top5 <- filter(filt_coal, 
               Entity=='China'|Entity=='United States'|Entity=='Russia'|Entity =='Australia'|Entity =='India')

options(repr.plot.width=8, repr.plot.height=4)

ggplot(top5, aes(x = Year, y = Coal.production..TWh., col = Entity)) +
    geom_point(size = 1) +
    geom_line() +
    labs(title = "Coal production", subtitle='Evolution of coal production for the top 5 world producers from 1970') +
    theme_light() + 
    scale_x_continuous(name = "Year") +
    scale_y_continuous(name="Coal production [TW/hr]", breaks=seq(0,25000,5000)) +
    theme(aspect.ratio=9/16)
```

**5.** Finally, let's make a plot with the cumulative sum of the World's coal production over the years. Again, we create a tibble `world` in which we consider only the entries which have `Entity == 'World'` and add a column with the cumulative sum of coal production with `mutate()`.

```{r}
world <- filter(coal, Entity=='World') %>% mutate(Cumulative.production..TWh = cumsum(Coal.production..TWh.))

options(repr.plot.width=8, repr.plot.height=4)

ggplot(world, aes(x = Year, y = Cumulative.production..TWh)) +
    geom_point(size = 1, col = 'red') +
    geom_line(col='red') +
    labs(title = "Coal production", subtitle='Evolution of cumulative coal production in the world') +
    theme_light() + 
    scale_x_continuous(name = "Year") +
    scale_y_continuous(name="Cumulative production [TW/hr]", labels = scientific) +
    theme(aspect.ratio=9/16)
```

## Exercise 4 - Covid19 Vaccine data

The file `vaccinationsby-manufacturer.csv`, (https://github.com/owid/covid-19-data/blob/master/public/data/vaccinations/vaccinations-by-manufacturer.csv contains a summary on the vaccination data grouped by Vaccine type and Country.

1. `filter()` the original tibble by selecting the following countries: Italy.
2. Plot the number of vaccines given as a function of time for the different vaccine manufacturer.
3. From the same tibble plot the total number of vaccines shot per day in Italy
4. Do the same exercise for the following countries: Germany and United States of America

The file `vaccinations.csv`, (https://github.com/owid/covid-19-data/blob/master/public/data/vaccinations/vaccinations.csv) contains country-by-country data on global COVID-19 vaccinations. The dataset includes some subnational locations (England, Northern Ireland, Scotland, Wales, : : :) and international aggregates (World, continents, European Union ldots). 
They can be identifed by their iso code that starts with OWID

1. Selecting all the European countries in the tibble, plot the number of daily vaccinations per million as a function of date
2. Study the data structure and produce few relevant plots of your taste


### Solution

Firtly, let's import the first dataset using the `read.csv()` function and save the data in a tibble.

```{r}
data3 <- read.csv("vaccinations-by-manufacturer.csv", header = TRUE)
vacc <- tibble(data3)
```

**1.** Now we can use `filter()` to keep only the data related to Italy.

```{r}
filt_italy <- filter(vacc, location == 'Italy') # Select entries only about Italy

class(filt_italy$date) # The column 'date' is read as factor 
filt_italy$date <- as.Date(filt_italy$date) #Convert it to Date type
class(filt_italy$date) 

head(filt_italy)
tail(filt_italy)
```

**2.** Now let's plot the number of vaccines given as a function of time for the different vaccine manufacturer.

```{r}
options(repr.plot.width=8, repr.plot.height=4)

ggplot(filt_italy, aes(x = date, y = total_vaccinations, col = vaccine)) +
    geom_point(size = 0.8) +
    geom_line(size = 0.3) +
    labs(title = "Covid-19 vaccine campaign in Italy", subtitle='Shots of vaccine erogated in Italy per day by manufacter') +
    theme_light() + 
    theme(axis.line = element_line(size = 0.3, linetype = "solid"), 
          axis.ticks.length=unit(.25, "cm")) +
    scale_x_date(name = "Date",
                 breaks = function(x) seq.Date(from = min(x), to = max(x), by = "2 weeks"), 
                 labels = date_format("%d-%m-%Y"), 
                 minor_breaks = function(x) seq.Date(from = min(x), to = max(x), by = "2 days")) +
    scale_y_continuous(name= "Total vaccinations", breaks=seq(0,8e6, 1e6)) +
    theme(aspect.ratio=9/16)
```

**3.** Now to plot the total number of vaccines shot per day in Italy we use `sum()` on the column `total_vaccination` grouping data by `date` with `group_by`. Then we can perform the plot.

```{r}
tot.vacc.it <- filt_italy %>% group_by(date) %>% summarise(total_vaccinations = sum(total_vaccinations)) # Sum by Date

head(tot.vacc.it)
```

```{r}
options(repr.plot.width=8, repr.plot.height=4)

ggplot(tot.vacc.it, aes(x = date, y = total_vaccinations)) +
    geom_point(size = 0.8, col = 'mediumvioletred') +
    geom_line(size = 0.5, col = 'mediumvioletred') +
    labs(title = "Covid-19 vaccine campaign in Italy", subtitle='Total shots of vaccine erogated in Italy per day') +
    theme_light() + 
    theme(axis.line = element_line(size = 0.3, linetype = "solid"), 
          axis.ticks.length=unit(.25, "cm")) +
    scale_x_date(name = "Date",
                 breaks = function(x) seq.Date(from = min(x), to = max(x), by = "2 weeks"), 
                 labels = date_format("%d-%m-%Y"), 
                 minor_breaks = function(x) seq.Date(from = min(x), to = max(x), by = "2 days")) +
    scale_y_continuous(name= "Total vaccinations", breaks=seq(0,1.2e7, 1e6)) +
    theme(aspect.ratio=9/16)
```

**4.** Now we repeat the same procedure for Germany and the USA.

```{r}
filt_germ <- filter(vacc, location == 'Germany')                 # Select entries only about Germany
filt_USA <- filter(vacc, location == 'United States') # Select entries only about USA

# Convert data colums to Date type
filt_germ$date <- as.Date(filt_germ$date)
filt_USA$date <- as.Date(filt_USA$date)

head(filt_germ)
head(filt_USA)
```

```{r}
# Compute total daily vaccines

tot.vacc.de <- filt_germ %>% group_by(date) %>% summarise(tot_daily_vacc = sum(total_vaccinations))
tot.vacc.us <- filt_USA %>% group_by(date) %>% summarise(tot_daily_vacc = sum(total_vaccinations)) 

head(tot.vacc.de)
head(tot.vacc.us)
```

```{r}
# Plot for Germany

options(repr.plot.width=8, repr.plot.height=4)

ggplot() +
    geom_point(data = filt_germ, aes(x = date, y = total_vaccinations, col = vaccine), size = 0.8) +
    geom_point(data = tot.vacc.de, aes(x = date, y = tot_daily_vacc, col = 'Total'), size = 0.8) +           
    geom_line(data = filt_germ, aes(x = date, y = total_vaccinations, col = vaccine), size = 0.5) +
    geom_line(data = tot.vacc.de, aes(x = date, y = tot_daily_vacc, col = 'Total'), size = 0.5) +
    labs(title = "Covid-19 vaccine campaign in Germany", subtitle='Shots of vaccine erogated in Germany per day by manufacter') +
    theme_light() + 
    theme(axis.line = element_line(size = 0.3, linetype = "solid"), 
          axis.ticks.length=unit(.25, "cm")) +
    scale_x_date(name = "Date",
                 breaks = function(x) seq.Date(from = min(x), to = max(x), by = "2 weeks"), 
                 labels = date_format("%d-%m-%Y"), 
                 minor_breaks = function(x) seq.Date(from = min(x), to = max(x), by = "2 days")) +
    scale_y_continuous(name= "Total vaccinations", breaks=seq(0, 2e7, 2e6)) +
    theme(aspect.ratio=9/16)
```

```{r}
# Plot for the US

options(repr.plot.width=8, repr.plot.height=4)

ggplot() +
    geom_point(data = filt_USA, aes(x = date, y = total_vaccinations, col = vaccine), size = 0.8) +
    geom_point(data = tot.vacc.us, aes(x = date, y = tot_daily_vacc, col = 'Total'), size = 0.8) +           
    geom_line(data = filt_USA, aes(x = date, y = total_vaccinations, col = vaccine), size = 0.5) +
    geom_line(data = tot.vacc.us, aes(x = date, y = tot_daily_vacc, col = 'Total'), size = 0.5) +
    labs(title = "Covid-19 vaccine campaign in USA", subtitle='Shots of vaccine erogated in the United States per day by manufacter') +
    theme_light() + 
    theme(axis.line = element_line(size = 0.3, linetype = "solid"), 
          axis.ticks.length=unit(.25, "cm")) +
    scale_x_date(name = "Date",
                 breaks = function(x) seq.Date(from = min(x), to = max(x), by = "2 weeks"), 
                 labels = date_format("%d-%m-%Y"), 
                 minor_breaks = function(x) seq.Date(from = min(x), to = max(x), by = "2 days")) +
    scale_y_continuous(name= "Total vaccinations", breaks=seq(0, 2.2e8, 2e7)) +
    theme(aspect.ratio=9/16)
```

Now let's import the second dataset in the usual way.

```{r}
data4 <- read.csv("vaccinations.csv", header = TRUE)
vacc2 <- tibble(data4)
head(vacc2)
```

**1.** To keep only the members of the european union one can use `filter()` to select them using their iso code. Then we convert the `date` column from `factor` to `Date` type. Finally we can plot the number of daily vaccinations per million as a function of date. To make the graph more readable we split the countries into 3 groups and make 3 plots.

```{r}
vacc2$date <- as.Date(vacc2$date) #Convert date to Data type

eu_iso1 <- c('AUT', 'BEL', 'BGR', 'HRV', 'CYP', 'CZE', 'DNK', 'EST', 'FIN')  #EU members
eu_iso2 <- c('FRA', 'DEU', 'GRC', 'HUN', 'IRL', 'MLT', 'LVA', 'LTU', 'LUX') 
eu_iso3 <- c('ITA', 'NLD', 'POL', 'PRT', 'ROU', 'SVK', 'SVN', 'ESP', 'SWE')

EU_data1 <- filter(vacc2, iso_code %in% eu_iso1)
EU_data2 <- filter(vacc2, iso_code %in% eu_iso2)
EU_data3 <- filter(vacc2, iso_code %in% eu_iso3)

head(EU_data1)
head(EU_data2)
head(EU_data3)
```

```{r}
options(repr.plot.width= 8, repr.plot.height= 10)

#Define function to make the plot

eu_plot <- function(tibb) {
            plt <- (ggplot(tibb, aes(x = date, y = daily_vaccinations_per_million, col = location)) +
                        geom_point(size = 0.8) +
                        geom_line(size = 0.5) +
                        theme_light() + 
                        theme(axis.line = element_line(size = 0.3, linetype = "solid"), axis.ticks.length=unit(.25, "cm")) +
                        scale_x_date(name = NULL,
                               breaks = function(x) seq.Date(from = min(x), to = max(x), by = "2 weeks"), 
                               labels = date_format("%d-%m-%Y"), 
                               minor_breaks = function(x) seq.Date(from = min(x), to = max(x), by = "2 days")) +
                        scale_y_continuous(name= NULL) +
                        theme(aspect.ratio=9/16))                    
            return(plt)
            }

plt1 <- eu_plot(EU_data1)
plt2 <- eu_plot(EU_data2)
plt3 <- eu_plot(EU_data3)

figure <- ggarrange(plt1, plt2, plt3, ncol = 1, nrow = 3) +                 
                    labs(title = "Covid-19 vaccine campaign in EU", 
                         subtitle='Daily vaccinations per million erogated in the European Union')
annotate_figure(figure,
               top = text_grob("Covid-19 vaccine campaign in EU", 
                                face = "bold", size = 14, hjust = 0.6),
               bottom = text_grob("Date", size = 14, x = 0.4),
               left = text_grob("Daily vaccinations per million", rot = 90, size = 14, x = 2.5),
              )   
```

**2.** The tibble has 12 columns containing the following pieces of information:

* **`location`**: name of the country (or region within a country);
* **`iso_code`**: ISO 3166-1 alpha-3 – three-letter country codes;
* **`date`**: date of the observation;
* **`total_vaccinations`**: total number of doses administered. This is counted as a single dose, and may not equal the total number of people vaccinated, depending on the specific dose regime (e.g. people receive multiple doses). If a person receives one dose of the vaccine, this metric goes up by 1. If they receive a second dose, it goes up by 1 again.
* **`people_vaccinated`**: total number of people who received at least one vaccine dose. If a person receives the first dose of a 2-dose vaccine, this metric goes up by 1. If they receive the second dose, the metric stays the same.
* **`people_fully_vaccinated`**: total number of people who received all doses prescribed by the vaccination protocol. If a person receives the first dose of a 2-dose vaccine, this metric stays the same. If they receive the second dose, the metric goes up by 1.
* **`daily_vaccinations_raw`**: daily change in the total number of doses administered. It is only calculated for consecutive days. This is a raw measure provided for data checks and transparency.
* **`daily_vaccinations`**: new doses administered per day (7-day smoothed). For countries that don't report data on a daily basis, it has been assumed that doses changed equally on a daily basis over any periods in which no data was reported. This produces a complete series of daily figures, which is then averaged over a rolling 7-day window. 
* **`total_vaccinations_per_hundred`**: `total_vaccinations` per 100 people in the total population of the country
* **`people_vaccinated_per_hundred`**: `people_vaccinated` per 100 people in the total population of the country.
* **`people_fully_vaccinated_per_hundred`**: `people_fully_vaccinated` per 100 people in the total population of the country.
* **`daily_vaccinations_per_million`**: `daily_vaccinations` per 1,000,000 people in the total population of the country.  

Row-wise, data is stored in chronological order by country (in alphabetical order).

```{r}
# Put data back together

EU <- rbind(EU_data1, EU_data2, EU_data3)

str(EU)
head(EU)
```

Some interesting plots might be for example a comparison between the temporal evolution of `total_vaccinations`, `people_vaccinated`and `people_fully_vaccinated` for example in Italy.

```{r}
it <- filter(EU, location == 'Italy')
it <- select(it, date, total_vaccinations, people_vaccinated, people_fully_vaccinated)
it <- melt(it,  id.vars = 'date', variable.name = 'Legend')


options(repr.plot.width=8, repr.plot.height=4)

ggplot(it, aes(date, value)) +
    geom_point(aes(col = Legend), size = 0.8) +
    geom_line(aes(col = Legend), size = 0.5) + 
    labs(title = "Covid-19 vaccine campaign in Italy", subtitle='Daily doses of vaccine and number of fully vaccinated people') +
    theme_light() + 
    theme(axis.line = element_line(size = 0.3, linetype = "solid"), 
          axis.ticks.length=unit(.25, "cm")) +
    scale_x_date(name = "Date",
                 breaks = function(x) seq.Date(from = min(x), to = max(x), by = "2 weeks"), 
                 labels = date_format("%d-%m-%Y"), 
                 minor_breaks = function(x) seq.Date(from = min(x), to = max(x), by = "2 days")) +
    scale_y_continuous(name= NULL, breaks=seq(0, 1e7, 2e6)) +

    theme(aspect.ratio=9/16)


```

It might also be interesting to compare the number of fully vaccinated people per hundred between the different EU countries for example with a barplot.

```{r}
tot_vac_EU <- EU %>% group_by(location) %>% summarise(tot_vac = max(people_fully_vaccinated_per_hundred, na.rm = T))

options(repr.plot.width=6, repr.plot.height=6)

ggplot(tot_vac_EU, aes(x = location, y = tot_vac, fill = location)) +
    geom_bar(stat ='identity', colour="black")+
    coord_flip()+
    scale_y_continuous(name = "% of fully vaccinated people") +
    labs(title = "Covid-19 vaccine campaign in EU", 
         subtitle='Percentage of fully vaccinated people in EU member states') +
    guides(fill=FALSE)+
    theme_minimal()

```

```{r}

```
